BivData Setup

### 2020-02-03 doc/Bivalent_Analysis.Rmd
moved some DF setup from analysis to set up script

```{r WSB.SC, echo=FALSE}
#make the dataset
WSB.Bivalents.DF <- Curated_BivData[Curated_BivData$strain == "WSB",]
#correct and remove, 26dec17_18nov17_WSB_f4_sp1_12_rev_28, 26dec17_18nov17_WSB_f4_sp1_12_rev_27
table(WSB.Bivalents.DF$sex, WSB.Bivalents.DF$hand.foci.count)

@@

```{r LEW.SC, echo=FALSE}
#make the dataset
LEW.Bivalents.DF <- Curated_BivData[Curated_BivData$strain == "LEW",]
table(LEW.Bivalents.DF$sex, LEW.Bivalents.DF$hand.foci.count)

#plot the differences
LEW.ploty <- ggplot(LEW.Bivalents.DF,  aes(y=chromosomeLength, x = sex, color= as.factor(hand.foci.count)))+geom_jitter()+ggtitle("")

LEW.ploty
#remove the NAs

#make a table of the means and n ect
LEW.SC.table <- ddply(LEW.Bivalents.DF, c("sex"), summarise,
                             mean_SC = mean(chromosomeLength),
                              n_SC = length(Obj.ID),

```{r G.SC, echo=FALSE}
#make the dataset
G.Bivalents.DF <- Curated_BivData[Curated_BivData$strain == "G",]
table(G.Bivalents.DF$sex, G.Bivalents.DF$hand.foci.count)

#plot the differences
G.ploty <- ggplot(G.Bivalents.DF,  aes(y=chromosomeLength, x = sex, color= as.factor(hand.foci.count)))+geom_jitter()+ggtitle("")

G.ploty
#remove the NAs

#make a table of the means and n ect
G.SC.table <- ddply(G.Bivalents.DF, c("sex"), summarise,
                             mean_SC = mean(chromosomeLength),
                              n_SC = length(Obj.ID),

```{r PWD.SC, echo=FALSE}
#make the dataset
PWD.Bivalents.DF <- Curated_BivData[Curated_BivData$strain == "PWD",]
table(PWD.Bivalents.DF$sex, PWD.Bivalents.DF$hand.foci.count)

#plot the differences
PWD.ploty <- ggplot(PWD.Bivalents.DF,  aes(y=chromosomeLength, x = sex, color= as.factor(hand.foci.count)))+geom_jitter()+ggtitle("")

PWD.ploty
#remove the NAs

#make a table of the means and n ect
PWD.SC.table <- ddply(PWD.Bivalents.DF, c("sex"), summarise,
                             mean_SC = mean(chromosomeLength),
                              n_SC = length(Obj.ID),

```{r KAZ.SC, echo=FALSE}
#make the dataset
KAZ.Bivalents.DF <- Curated_BivData[Curated_BivData$strain == "KAZ",]
table(KAZ.Bivalents.DF$sex, KAZ.Bivalents.DF$hand.foci.count)

#plot the differences
KAZ.ploty <- ggplot(KAZ.Bivalents.DF,  aes(y=chromosomeLength, x = sex, color= as.factor(hand.foci.count)))+geom_jitter()+ggtitle("")

KAZ.ploty
#remove the NAs

#make a table of the means and n ect
KAZ.SC.table <- ddply(KAZ.Bivalents.DF, c("sex"), summarise,
                             mean_SC = mean(chromosomeLength),
                              n_SC = length(Obj.ID),

```{r SKIVE.Sc, echo=FALSE}
#make the dataset
SKIVE.Bivalents.DF <- Curated_BivData[Curated_BivData$strain == "SKIVE",]
table(SKIVE.Bivalents.DF$sex, SKIVE.Bivalents.DF$hand.foci.count)

#plot the differences
SKIVE.ploty <- ggplot(SKIVE.Bivalents.DF,  aes(y=chromosomeLength, x = sex, color= as.factor(hand.foci.count)))+geom_jitter()+ggtitle("")

SKIVE.ploty
#remove the NAs

#make a table of the means and n ect
SKIVE.SC.table <- ddply(SKIVE.Bivalents.DF, c("sex"), summarise,
                             mean_SC = mean(chromosomeLength),
                              n_SC = length(Obj.ID),

```{r MSM.SC, echo=FALSE}
#make the dataset
MSM.Bivalents.DF <- Curated_BivData[Curated_BivData$strain == "MSM",]
table(MSM.Bivalents.DF$sex, MSM.Bivalents.DF$hand.foci.count)

MSM.ploty
#remove the NAs

#make a table of the means and n ect
MSM.SC.table <- ddply(MSM.Bivalents.DF, c("sex"), summarise,
                             mean_SC = mean(chromosomeLength),
                              n_SC = length(Obj.ID),

```{r MOLF.SC, eval=FALSE}
#make the dataset
MOLF.Bivalents.DF <- Curated_BivData[Curated_BivData$strain == "MOLF",]
table(MOLF.Bivalents.DF$sex, MOLF.Bivalents.DF$hand.foci.count)

MOLF.ploty
#remove the NAs

#make a table of the means and n ect
MOLF.SC.table <- ddply(MOLF.Bivalents.DF, c("sex"), summarise,
                             mean_SC = mean(chromosomeLength),
                              n_SC = length(Obj.ID),

>>>>

(adding all of these blocks to -- the setup script); strain.Bivalents.DF

```{r WSB.SC, echo=FALSE, eval=FALSE}
#make the dataset
WSB.Bivalents.DF <- Curated_BivData[Curated_BivData$strain == "WSB",]
#correct and remove, 26dec17_18nov17_WSB_f4_sp1_12_rev_28, 26dec17_18nov17_WSB_f4_sp1_12_rev_27
table(WSB.Bivalents.DF$sex, WSB.Bivalents.DF$hand.foci.count)

@@

### 2020-02-03 src/BivData_Setup.Rmd
moved some DF setup from analysis to set up script

>>>>

## Strain specific data sets

Compile dataframes for both sexes of each strain.

```{r WSB.SC, echo=FALSE}
#make the dataset
WSB.Bivalents.DF <- Curated_BivData[Curated_BivData$strain == "WSB",]
#correct and remove, 26dec17_18nov17_WSB_f4_sp1_12_rev_28, 26dec17_18nov17_WSB_f4_sp1_12_rev_27
table(WSB.Bivalents.DF$sex, WSB.Bivalents.DF$hand.foci.count)

#plot the differences
wsb.ploty <- ggplot(WSB.Bivalents.DF,  aes(y=chromosomeLength, x = sex, color= as.factor(hand.foci.count)))+geom_jitter()
wsb.ploty

#make a table of the means and n ect
wsb.SC.table <- ddply(WSB.Bivalents.DF, c("sex"), summarise,
                             mean_SC = mean(chromosomeLength),
                              n_SC = length(Obj.ID),

                   mean.SC_0CO = mean(chromosomeLength[which(hand.foci.count == 0)], na.rm = TRUE),
                  n_0CO =  sum((hand.foci.count == 0), na.rm = TRUE ),
                 # CO2 = sum(hand.foci.count == 2, na.rm=TRUE),

                   mean.SC_1CO = mean(chromosomeLength[which(hand.foci.count == 1)], na.rm = TRUE),
                    n_1CO = sum((hand.foci.count == 1), na.rm = TRUE),

                   mean.SC_2CO = mean(chromosomeLength[which(hand.foci.count == 2)], na.rm = TRUE),
                   n_2CO = sum((hand.foci.count == 2), na.rm = TRUE),

                  mean.SC_3CO = mean(chromosomeLength[which(hand.foci.count == 3)], na.rm = TRUE),
                  n_3CO = sum((hand.foci.count == 3), na.rm = TRUE)

)
#can I plot these stats

#run a t.test
wsb.ttest  <- t.test(WSB.Bivalents.DF$chromosomeLength[WSB.Bivalents.DF$sex == "female"], WSB.Bivalents.DF$chromosomeLength[WSB.Bivalents.DF$sex == "male"])

```{r LEW.SC, echo=FALSE}
#make the dataset
LEW.Bivalents.DF <- Curated_BivData[Curated_BivData$strain == "LEW",]
table(LEW.Bivalents.DF$sex, LEW.Bivalents.DF$hand.foci.count)

#plot the differences
LEW.ploty <- ggplot(LEW.Bivalents.DF,  aes(y=chromosomeLength, x = sex, color= as.factor(hand.foci.count)))+geom_jitter()+ggtitle("")

LEW.ploty
#remove the NAs

#make a table of the means and n ect
LEW.SC.table <- ddply(LEW.Bivalents.DF, c("sex"), summarise,
                             mean_SC = mean(chromosomeLength),
                              n_SC = length(Obj.ID),

                   mean.SC_0CO = mean(chromosomeLength[which(hand.foci.count == 0)], na.rm = TRUE),
                  n_0CO =  sum((hand.foci.count == 0), na.rm = TRUE ),
                 # CO2 = sum(hand.foci.count == 2, na.rm=TRUE),

                   mean.SC_1CO = mean(chromosomeLength[which(hand.foci.count == 1)], na.rm = TRUE),
                    n_1CO = sum((hand.foci.count == 1), na.rm = TRUE),

                   mean.SC_2CO = mean(chromosomeLength[which(hand.foci.count == 2)], na.rm = TRUE),
                   n_2CO = sum((hand.foci.count == 2), na.rm = TRUE),

                  mean.SC_3CO = mean(chromosomeLength[which(hand.foci.count == 3)], na.rm = TRUE),
                  n_3CO = sum((hand.foci.count == 3), na.rm = TRUE)

)
#can I plot these stats

#run a t.test seperate out by the chrm classes
LEW.ttest  <- t.test(LEW.Bivalents.DF$chromosomeLength[LEW.Bivalents.DF$sex == "female"], LEW.Bivalents.DF$chromosomeLength[LEW.Bivalents.DF$sex == "male"])

```{r G.SC, echo=FALSE}
#make the dataset
G.Bivalents.DF <- Curated_BivData[Curated_BivData$strain == "G",]
table(G.Bivalents.DF$sex, G.Bivalents.DF$hand.foci.count)

#plot the differences
G.ploty <- ggplot(G.Bivalents.DF,  aes(y=chromosomeLength, x = sex, color= as.factor(hand.foci.count)))+geom_jitter()+ggtitle("")

G.ploty
#remove the NAs

#make a table of the means and n ect
G.SC.table <- ddply(G.Bivalents.DF, c("sex"), summarise,
                             mean_SC = mean(chromosomeLength),
                              n_SC = length(Obj.ID),

                   mean.SC_0CO = mean(chromosomeLength[which(hand.foci.count == 0)], na.rm = TRUE),
                  n_0CO =  sum((hand.foci.count == 0), na.rm = TRUE ),
                 # CO2 = sum(hand.foci.count == 2, na.rm=TRUE),

                   mean.SC_1CO = mean(chromosomeLength[which(hand.foci.count == 1)], na.rm = TRUE),
                    n_1CO = sum((hand.foci.count == 1), na.rm = TRUE),

                   mean.SC_2CO = mean(chromosomeLength[which(hand.foci.count == 2)], na.rm = TRUE),
                   n_2CO = sum((hand.foci.count == 2), na.rm = TRUE),

                  mean.SC_3CO = mean(chromosomeLength[which(hand.foci.count == 3)], na.rm = TRUE),
                  n_3CO = sum((hand.foci.count == 3), na.rm = TRUE)

)
#can I plot these stats

#run a t.test seperate out by the chrm classes
G.ttest  <- t.test(G.Bivalents.DF$chromosomeLength[G.Bivalents.DF$sex == "female"], G.Bivalents.DF$chromosomeLength[G.Bivalents.DF$sex == "male"])

```{r PWD.SC, echo=FALSE}
#make the dataset
PWD.Bivalents.DF <- Curated_BivData[Curated_BivData$strain == "PWD",]
table(PWD.Bivalents.DF$sex, PWD.Bivalents.DF$hand.foci.count)

#plot the differences
PWD.ploty <- ggplot(PWD.Bivalents.DF,  aes(y=chromosomeLength, x = sex, color= as.factor(hand.foci.count)))+geom_jitter()+ggtitle("")

PWD.ploty
#remove the NAs

#make a table of the means and n ect
PWD.SC.table <- ddply(PWD.Bivalents.DF, c("sex"), summarise,
                             mean_SC = mean(chromosomeLength),
                              n_SC = length(Obj.ID),

                   mean.SC_0CO = mean(chromosomeLength[which(hand.foci.count == 0)], na.rm = TRUE),
                  n_0CO =  sum((hand.foci.count == 0), na.rm = TRUE ),
                 # CO2 = sum(hand.foci.count == 2, na.rm=TRUE),

                   mean.SC_1CO = mean(chromosomeLength[which(hand.foci.count == 1)], na.rm = TRUE),
                    n_1CO = sum((hand.foci.count == 1), na.rm = TRUE),

                   mean.SC_2CO = mean(chromosomeLength[which(hand.foci.count == 2)], na.rm = TRUE),
                   n_2CO = sum((hand.foci.count == 2), na.rm = TRUE),

                  mean.SC_3CO = mean(chromosomeLength[which(hand.foci.count == 3)], na.rm = TRUE),
                  n_3CO = sum((hand.foci.count == 3), na.rm = TRUE)

)
#can I plot these stats

#run a t.test seperate out by the chrm classes
PWD.ttest  <- t.test(PWD.Bivalents.DF$chromosomeLength[PWD.Bivalents.DF$sex == "female"], PWD.Bivalents.DF$chromosomeLength[PWD.Bivalents.DF$sex == "male"])

```{r KAZ.SC, echo=FALSE}
#make the dataset
KAZ.Bivalents.DF <- Curated_BivData[Curated_BivData$strain == "KAZ",]
table(KAZ.Bivalents.DF$sex, KAZ.Bivalents.DF$hand.foci.count)

#plot the differences
KAZ.ploty <- ggplot(KAZ.Bivalents.DF,  aes(y=chromosomeLength, x = sex, color= as.factor(hand.foci.count)))+geom_jitter()+ggtitle("")

KAZ.ploty
#remove the NAs

#make a table of the means and n ect
KAZ.SC.table <- ddply(KAZ.Bivalents.DF, c("sex"), summarise,
                             mean_SC = mean(chromosomeLength),
                              n_SC = length(Obj.ID),

                   mean.SC_0CO = mean(chromosomeLength[which(hand.foci.count == 0)], na.rm = TRUE),
                  n_0CO =  sum((hand.foci.count == 0), na.rm = TRUE ),
                 # CO2 = sum(hand.foci.count == 2, na.rm=TRUE),

                   mean.SC_1CO = mean(chromosomeLength[which(hand.foci.count == 1)], na.rm = TRUE),
                    n_1CO = sum((hand.foci.count == 1), na.rm = TRUE),

                   mean.SC_2CO = mean(chromosomeLength[which(hand.foci.count == 2)], na.rm = TRUE),
                   n_2CO = sum((hand.foci.count == 2), na.rm = TRUE),

                  mean.SC_3CO = mean(chromosomeLength[which(hand.foci.count == 3)], na.rm = TRUE),
                  n_3CO = sum((hand.foci.count == 3), na.rm = TRUE)

)
#can I plot these stats

#run a t.test seperate out by the chrm classes
KAZ.ttest  <- t.test(KAZ.Bivalents.DF$chromosomeLength[KAZ.Bivalents.DF$sex == "female"], KAZ.Bivalents.DF$chromosomeLength[KAZ.Bivalents.DF$sex == "male"])

```{r SKIVE.Sc, echo=FALSE}
#make the dataset
SKIVE.Bivalents.DF <- Curated_BivData[Curated_BivData$strain == "SKIVE",]
table(SKIVE.Bivalents.DF$sex, SKIVE.Bivalents.DF$hand.foci.count)

#plot the differences
SKIVE.ploty <- ggplot(SKIVE.Bivalents.DF,  aes(y=chromosomeLength, x = sex, color= as.factor(hand.foci.count)))+geom_jitter()+ggtitle("")

SKIVE.ploty
#remove the NAs

#make a table of the means and n ect
SKIVE.SC.table <- ddply(SKIVE.Bivalents.DF, c("sex"), summarise,
                             mean_SC = mean(chromosomeLength),
                              n_SC = length(Obj.ID),

                   mean.SC_0CO = mean(chromosomeLength[which(hand.foci.count == 0)], na.rm = TRUE),
                  n_0CO =  sum((hand.foci.count == 0), na.rm = TRUE ),
                 # CO2 = sum(hand.foci.count == 2, na.rm=TRUE),

                   mean.SC_1CO = mean(chromosomeLength[which(hand.foci.count == 1)], na.rm = TRUE),
                    n_1CO = sum((hand.foci.count == 1), na.rm = TRUE),

                   mean.SC_2CO = mean(chromosomeLength[which(hand.foci.count == 2)], na.rm = TRUE),
                   n_2CO = sum((hand.foci.count == 2), na.rm = TRUE),

                  mean.SC_3CO = mean(chromosomeLength[which(hand.foci.count == 3)], na.rm = TRUE),
                  n_3CO = sum((hand.foci.count == 3), na.rm = TRUE)

)
#can I plot these stats

#run a t.test seperate out by the chrm classes
SKIVE.ttest  <- t.test(SKIVE.Bivalents.DF$chromosomeLength[SKIVE.Bivalents.DF$sex == "female"], SKIVE.Bivalents.DF$chromosomeLength[SKIVE.Bivalents.DF$sex == "male"])

```{r MSM.SC, echo=FALSE}
#make the dataset
MSM.Bivalents.DF <- Curated_BivData[Curated_BivData$strain == "MSM",]
table(MSM.Bivalents.DF$sex, MSM.Bivalents.DF$hand.foci.count)

#plot the differences
MSM.ploty <- ggplot(MSM.Bivalents.DF,  aes(y=chromosomeLength, x = sex, color= as.factor(hand.foci.count)))+geom_jitter()+ggtitle("")

MSM.ploty
#remove the NAs

#make a table of the means and n ect
MSM.SC.table <- ddply(MSM.Bivalents.DF, c("sex"), summarise,
                             mean_SC = mean(chromosomeLength),
                              n_SC = length(Obj.ID),

                   mean.SC_0CO = mean(chromosomeLength[which(hand.foci.count == 0)], na.rm = TRUE),
                  n_0CO =  sum((hand.foci.count == 0), na.rm = TRUE ),
                 # CO2 = sum(hand.foci.count == 2, na.rm=TRUE),

                   mean.SC_1CO = mean(chromosomeLength[which(hand.foci.count == 1)], na.rm = TRUE),
                    n_1CO = sum((hand.foci.count == 1), na.rm = TRUE),

                   mean.SC_2CO = mean(chromosomeLength[which(hand.foci.count == 2)], na.rm = TRUE),
                   n_2CO = sum((hand.foci.count == 2), na.rm = TRUE),

                  mean.SC_3CO = mean(chromosomeLength[which(hand.foci.count == 3)], na.rm = TRUE),
                  n_3CO = sum((hand.foci.count == 3), na.rm = TRUE)

)
#can I plot these stats

#run a t.test seperate out by the chrm classes
MSM.ttest  <- t.test(MSM.Bivalents.DF$chromosomeLength[MSM.Bivalents.DF$sex == "female"], MSM.Bivalents.DF$chromosomeLength[MSM.Bivalents.DF$sex == "male"])

```{r MOLF.SC, eval=FALSE}
#make the dataset
MOLF.Bivalents.DF <- Curated_BivData[Curated_BivData$strain == "MOLF",]
table(MOLF.Bivalents.DF$sex, MOLF.Bivalents.DF$hand.foci.count)

#plot the differences
MOLF.ploty <- ggplot(MOLF.Bivalents.DF,  aes(y=chromosomeLength, x = sex, color= as.factor(hand.foci.count)))+geom_jitter()+ggtitle("")

MOLF.ploty
#remove the NAs

#make a table of the means and n ect
MOLF.SC.table <- ddply(MOLF.Bivalents.DF, c("sex"), summarise,
                             mean_SC = mean(chromosomeLength),
                              n_SC = length(Obj.ID),

                   mean.SC_0CO = mean(chromosomeLength[which(hand.foci.count == 0)], na.rm = TRUE),
                  n_0CO =  sum((hand.foci.count == 0), na.rm = TRUE ),
                 # CO2 = sum(hand.foci.count == 2, na.rm=TRUE),

                   mean.SC_1CO = mean(chromosomeLength[which(hand.foci.count == 1)], na.rm = TRUE),
                    n_1CO = sum((hand.foci.count == 1), na.rm = TRUE),

                   mean.SC_2CO = mean(chromosomeLength[which(hand.foci.count == 2)], na.rm = TRUE),
                   n_2CO = sum((hand.foci.count == 2), na.rm = TRUE),

                  mean.SC_3CO = mean(chromosomeLength[which(hand.foci.count == 3)], na.rm = TRUE),
                  n_3CO = sum((hand.foci.count == 3), na.rm = TRUE)

)
#can I plot these stats

#run a t.test seperate out by the chrm classes
MOLF.ttest  <- t.test(MOLF.Bivalents.DF$chromosomeLength[MOLF.Bivalents.DF$sex == "female"], MOLF.Bivalents.DF$chromosomeLength[MOLF.Bivalents.DF$sex == "male"])
